A GRASP algorithm for the concrete delivery problem.

### 2023-11-29 Article/cdp_content.tex
Save

\documentclass{article}
% \documentclass[review]{elsarticle}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage[algo2e,noend]{algorithm2e}
\usepackage[compatible,noend]{algpseudocode}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{bbding}
\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{tikz}
\usepackage{subcaption}
\usetikzlibrary{automata, topaths, calc, positioning, shapes, backgrounds, fit, matrix}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{datatool}
\usepackage{array}
\usepackage{pgfplotstable}
\pgfplotsset{width=7cm,compat=newest}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}
\usepackage{multirow}
\usepackage{float}
\usepackage[text={15cm,21cm},centering]{geometry}
\usepackage{setspace}
\usepackage{array}
\allowdisplaybreaks
\usepackage{lineno}
\usepackage{tkz-graph}
\usepackage{breqn}

\tikzset{
base/.style = {shape=rectangle, 
                      anchor=center,minimum size=5mm, 
                     align=center,
                     top color=white, ,inner sep=0ex,
                     minimum size=5mm
                     },
    LC11/.style =   {  base,   
                    text width=3em, 
                    bottom color=brown!100,
                    },
    UC11/.style = {     base,    
                    text width=5em, 
                    bottom color=brown!100,
                    align = right,
                },
    LC12/.style =   {  base,   
                    text width=1em, 
                    bottom color=orange!100,
                    },
    UC12/.style = {     base,    
                    text width=2.5em, 
                    bottom color=orange!100,
                },
    LC21/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=brown!100,
                    },
    UC21/.style = {     base,    
                    text width=3.5em, 
                    bottom color=brown!100,
                },
    LC22/.style =   {  base,   
                    text width=4em, 
                    bottom color=blue!100,
                    },
    UC22/.style = {     base,    
                    text width=7em, 
                    bottom color=blue!100,
                    align = left,
                },
    UC221/.style = {     base,    
                    text width=3.5em, 
                    bottom color=blue!100,
                    % color=blue!100,
                    outer xsep=0em,
                    % align = right,
                },
                UC231/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=blue!100,
                    },
    LC23/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=orange!100,
                    },
    UC23/.style = {     base,    
                    text width=2.em, 
                    bottom color=orange!100,
                },
  env/.style      = {base, font=\ttfamily\normalsize},
label/.style   = {base,font=\ttfamily\normalsize, text width = 8em, 
  inner sep=0em, rounded corners=1mm,bottom color=red!80,},
  dummy/.style    = {circle,draw}
}
\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newcommand{\pcmaxc}{P$|\mbox{\em cont}|$C$_{\max}$\xspace}

\newcommand{\GRASP}{Greedy randomized adaptive search procedure\xspace}
\newcommand{\F}{$\mathcal{F}$\xspace}
\newcommand{\B}{$\mathcal{B}$\xspace}
\newcommand{\C}{$\mathcal{C}$\xspace}
\newcommand{\LB}{$\mathcal{L}$\xspace}
\newcommand{\Lb}{$\mathcal{L}_b$\xspace}
\newcommand{\D}{$\mathcal{D}$\xspace}
 \newcommand*{\red}{\textcolor{red}}

\renewcommand{\algorithmicforall}{\textbf{for each}}
\SetKwFor{ForEach}{for each}{}{}%
\renewcommand{\algorithmiccomment}[2][1\linewidth]{%
\leavevmode\hfill\makebox[#1][l]{/* \textbf{~#2} */}}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}

\renewcommand{\tabcolsep}{4pt}

\modulolinenumbers[1]
\linenumbers

\oddsidemargin=0.5in
\topmargin=-0.25in
\textwidth=5.5in
\textheight=8.25in

%\journal{European Journal of Operational Research}

%\begin{frontmatter}

\title{A GRASP algorithm for the concrete delivery problem. }
\author{Ousmane Ali$^{(1)}$, Jean-Fran\c cois C\^ot\'e$^{(2)}$, Leandro C.~Coelho$^{(3)}$\\
 $(1)$ {\tt nassoma-wattara-ousmane.ali.1@ulaval.ca}\\
 $(2)$ {\tt Jean-Francois.Cote@fsa.ulaval.ca}\\
 $(3)$ {\tt Leandro.Coelho@fsa.ulaval.ca}\\
}

% \date{\today}

\begin{document}
\maketitle
\begin{abstract}
    This paper addresses a novel variant of the Concrete Delivery Problem (CDP), which involves the efficient scheduling of ready-mixed concrete deliveries to construction sites while balancing the conflicting goals of minimizing transportation costs and maximizing customer satisfaction. In this study, we propose an exact formulation and a heuristic approach based on the Greedy Randomized Adaptive Search Procedure (GRASP), to tackle this challenging CDP variant. This variant introduces realistic side constraints, including driver working shifts, a minimum driver working time, and overtime penalties. Additionally, it considers the scenario where customers may request multiple types of concrete delivered within the same time window. We assess the performance of our heuristic using new public instances generated for this problem and provide a comparative analysis with another CDP variant to demonstrate its effectiveness.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
Concrete is a widely used building material in construction projects. Its perishable nature is affected by many factors that impact its quality \citep{sinha_quality_2021}, which is crucial for the durability and strength of the final construction. Concrete comes in two types: ready-mixed concrete (RMC) and site-mixed concrete (SMC). RMC is manufactured in a batch plant and delivered to the construction site, while SMC is produced on-site using raw materials stored on the construction site. Using SMC can avoid delays caused by road traffic, but it has a slower and more difficult production process, requires storage for mixing materials and equipment, and is suitable for low amounts of concrete. On the other hand, RMC has better quality and benefits from lower production costs \citep{muresan_comparing}. However, to take advantage of these benefits, the batch plant manager must ensure efficient and prompt delivery on the construction site, which may require a fleet of high-cost revolving drum trucks (concrete mixers) to dispatch the RMC.

@@

The rest of the paper is organized as follows: Section \ref{lit_review} provides a literature review of previous work related to the CDP. Section \ref{desc_form} provides a formal description and mathematical model of the problem. Section \ref{grasp_method} describes the GRASP algorithm and the constructive heuristics developed to solve this variant of the CDP. Section \ref{comp_exp} presents computational experiments and sensitivity analyses to evaluate the proposed approach, and finally, section \ref{concl} presents the conclusions.

\section{Literature review}
\label{lit_review}

@@

\section{Problem description}
\label{desc_form}
The focus of this paper is on the distribution of RMC from a Canadian company that operates in the greater Montreal area. When a customer places an order, it is received at a control center and immediately assigned to one of the company's batch plants. These plants produce the concrete and then deliver it to the customer. The problem we are examining involves a set of customer orders, a set of concrete-mixer drivers, and a set of batch plants.

% \subsection*{Customer orders}

@@

% \subsection*{Drivers}

@@

\begin{figure}[htbp]
    \centering

    \vspace*{-0mm}
    \begin{adjustbox}{max width=0.85\textwidth}
        \begin{tikzpicture}[-latex]
            \matrix (chart)
            [
            matrix of nodes, nodes in empty cells,
            column sep      = 0em,
            row sep         = 3ex,
            column 1/.style = {nodes={label}},    column 2/.style = {},       column 3/.style = {nodes={env}},      column 4/.style = {nodes={env}},         column 5/.style = {nodes={env}},         column 6/.style = {nodes={env}},           column 7/.style = {nodes={env}},           column 8/.style = {nodes={env}},           column 9/.style = {nodes={env}},           column 10/.style = {nodes={env}},         column 11/.style = {nodes={env}},           column 12/.style = {nodes={env}},    column 13/.style = {nodes={env}}
            ]
            {
            $C_2-D_2$ (1 m$^3$) &
            &   &   &   &   &   &   &   &   &   &   &   &            |[LC23]| L &            &       &     |[UC23]| U \\
            $C_2-D_1$ (3 m$^3$) &           &      &        &        &           &            &            &
            &
            &
            &
            |[LC21]| L &
            &
            &
            &
            |[UC21]| U &
            \\
            $C_2-D_3$ (11 m$^3$) &
            &
            &
            &
            &
            &
            |[LC22]| L &
            &
            &
            |[UC22]| &
            |[UC22]|U  &
            |[UC221]|  &
            &
            &
            &
            &
            \\
            $C_1-D_2$ (4 m$^3$) &
            &
            &
            &
            |[LC12]| L &
            &
            &
            &
            |[UC12]| U &
            &
            &
            &
            &
            &
            &
            &
            \\
            $C_1-D_1$ (8 m$^3$) &
            &
            |[LC11]| L &
            &
            &
            &
            |[UC11]|U &
            |[UC11]| &
            &
            &
            &
            &
            &
            &
            &
            &
            \\
            \vspace*{-10em}
            Start time &&
            06:21 &
            &
            06:40 &
            &
            07:00 &
            &
            07:16 &  07:25 &
            &
            07:43 &
            &
            07:51 &
            &
            08:02 & 08:08 \\
            };
            % \node[fit={(chart-3-10) (chart-3-12)},style=UC22]{U};
            \draw (chart-5-3) edge (chart-5-7);
            % \draw (chart-5-8.3) edge (chart-2-12);
            \draw  (chart-4-5) edge (chart-4-9);
            % \draw  (chart-4-9) edge (chart-1-14);
            \draw  (chart-3-7) edge (chart-3-10);
            \draw  (chart-2-12) edge (chart-2-16);
            \draw  (chart-1-14) edge (chart-1-17);

@@

\section{Constructive heuristics and GRASP}
\label{grasp_method}

@@

\section{Computational experiments}
\label{comp_exp}

In this section, we present and discuss the results of computational experiments conducted using the GRASP heuristic described in section~\ref{grasp_method}. The implementation of the GRASP algorithm is coded in C++. We run our experiments on the benchmark data used in \cite{kinable2014concrete}, and on a new dataset extracted from delivery operations records provided by our industry partner.

\subsection{Generation of instances}
\newcommand{\nbInstance}{36}
The dataset used in this section was obtained from our partner and contains records representing delivery operations from up to 8 production centers for $\nbInstance$ days. From this historical data, we extract information such as daily orders delivered, plant assignments to orders, and the number of available drivers. We created $\nbInstance$ instances from this data, where each instance corresponds to a daily operation. To maintain confidentiality, we have removed the GPS coordinates of customers and plants, but have included two matrices containing the distances and driving times between all plants and customers. An instance contains information such as each driver's capacity, associated batch plant, and shift start time (which we generate). For each customer, we have the due time, the total demand, the number of orders (type of concrete) received, and its index in the time (distance) matrix. For each order, we have its demand and the corresponding production plant. Finally, we have the loading capacity for each plant, and also its index in the time matrix. The name of an instance has the format $C\_k\_n\_o\_z$, where $k$ is the number of available drivers, $n$ is the number of customers, $o$ is the total number of daily orders, and $z$ is the number of plants. The dataset is divided into small, medium, and large sets according to the total number of daily orders. We have summarized the dataset in Table~\ref{tab:instances}. The dataset is available upon request as a contribution to the CDP literature.

\begin{table}[htpb]
    \centering
    \caption{Instances summary}
    \label{tab:instances}
    \small
    \resizebox*{0.8\textwidth}{!}{
        \begin{tabular}{lcccccc}
            \toprule
            {}     & \# & Demand            & \#Order   & \#Client & \#Driver & \#Depot \\
                   &    & (m$^3$)           &           &          &          &         \\
            \midrule
            Small  & 8  & 226.5 - 937.5     & 7 - 14    & 4 - 11   & 13-35    & 1-3     \\
            % \cmidrule{3-7}
            Medium & 14 & 1,160.5 - 2,971.0 & 43 - 98   & 40 - 89  & 76-137   & 6-8     \\
            % \cmidrule{3-7}
            Large  & 14 & 3,078. - 3,953.5  & 107 - 136 & 92 - 127 & 129-150  & 8       \\
            \bottomrule
        \end{tabular}
    }
\end{table}

@@

\cite{kinable2014concrete} provided a benchmark dataset for their variant of the $CDP$. Although their primary objective is to maximize the total load delivered each day, without considering loading operations at a plant and ensuring deliveries within specified time windows, we still use this dataset to analyze and compare the performance of our algorithm under different conditions. Table \ref*{tab:cdp_instances} shows the performance of the GRASP heuristic along with the other methods (CP, MIP, SD-heuristic, and Hybrid) used in \cite{kinable2014concrete}.  For each method, the table shows the average execution time in milliseconds and the corresponding gap between the obtained solution and the upper bound provided by \cite{kinable2014concrete}.

\begin{table}[htbp]
    \centering
    \caption{Performance of the GRASP heuristic on the CDP benchmark instances}
    \label{tab:cdp_instances}
    \scriptsize
    \resizebox{1\textwidth}{!}{
        \begin{tabular}{@{}cccccccccccc@{}}
            \toprule
                                   &     & \multicolumn{2}{c}{CP}     & \multicolumn{2}{c}{MIP}   & \multicolumn{2}{c}{SD-heuristic} & \multicolumn{2}{c}{Hybrid} & \multicolumn{2}{c}{GRASP}                                                            \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
                                   &     & Gap (\%)                   & Time (ms)                 & Gap (\%)                         & Time (ms)                  & Gap (\%)                   & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
            \multirow{2}{*}{Set A} & Avg & 4.2                        & 197,012                   & 7.3                              & 13,405,798                 & 9.1                        & 23        & 7.0      & 100,765   & 5.7      & 13,186    \\ \cmidrule(l){2-10} \cmidrule(l){11-12}
                                   & Opt & \multicolumn{2}{c}{40/64}  & \multicolumn{2}{c}{37/64} & \multicolumn{2}{c}{30/64}        & \multicolumn{2}{c}{35/64}  & \multicolumn{2}{c}{35/64}                                                            \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
            \multirow{2}{*}{Set B} & Avg & 12.1                       & 357,313                   & -                                & -                          & 16.3                       & 1,331     & -        & -         & 13.8     & 574,983   \\ \cmidrule(l){2-10} \cmidrule(l){11-12}
                                   & Opt & \multicolumn{2}{c}{55/128} & \multicolumn{2}{c}{-}     & \multicolumn{2}{c}{40/128}       & \multicolumn{2}{c}{-}      & \multicolumn{2}{c}{44/128}                                                           \\ \bottomrule
        \end{tabular}
    }
\end{table}

@@

The computational results of our instances solved with the GRASP heuristic are summarized in the tables below. %The stopping criteria are set to 20,000 iterations or 3600 seconds of running time (unless otherwise specified).
The parameters used in our experiments are listed in Table~\ref*{tab:problem_parameters}.

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
    \small
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter}  &
        \multicolumn{1}{c}{Value} \\ \midrule
 Time window ($\tau^w$)  & 60 min    \\
 Unloading duration ($\tau_c^u$)  & 2 min$/m^3$   \\
 Cleaning duration ($\rho$)    & 10 min  \\
        Adjustment duration ($\alpha$)                                                & 10 min                    \\
        Max travel time ($\Delta$)                                                    & 120 min                   \\
        Min working time ($M_T$)                                                      & 180 min                   \\
        Max working time ($N_T$)                                                      & 480 min                   \\
        Max overtime duration ($O_T$)                                                 & 120 min                   \\
        Max delay between two consecutive deliveries of the same order $\gamma^1$)   & 20 min                    \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min                    \\
        Penalty of unfulfilled orders ($\beta_1$)                                     & 10,0000                   \\
        Penalty of first delivery delay ($\beta_2$)                                   & 1,0000                    \\
        Penalty for driver underutilization  ($\beta_3$)                              & 30                        \\
        Driver overtime penalty $ (\beta_4$)                                          & 20                        \\
        \bottomrule
    \end{tabularx}
\end{table}

The table \ref*{tab:all_instances} contains the detailed results for all instances with a stop criterion of 3600 seconds. The table shows the demand of each instance, the average, and the best values of the objective function when solving each instance five times. All daily orders of the small instances are completely served by our algorithm within these five iterations, as shown in column $UQ$, which reports the undelivered quantity. For the medium and large instances, $99.57\%$ and $99.5\%$ of the total demands are delivered. The sum of driver underutilization costs ($DUC$) is high for medium and large instances. This indicates the underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase travel costs ($TC$).

@@

    \multirow[c]{14}{*}{Large} & C_132_98_109_8 & 3,078.5 & 22,994.6 & 0.0 & 465.5 & 496.5 & 3,804.8 & 579,471.0 & 22,712.7 & 0.0 & 351.5 & 56.2 & 803.2 & 4,011.3 & 478,549.4 \\
     & C_129_101_119_8 & 3,229.0 & 17,323.1 & 11.0 & 657.8 & 1,577.6 & 2,375.9 & 1,869,937.5 & 17,311.8 & 11.0 & 598.8 & 58.4 & 1,507.7 & 1,948.1 & 1,800,315.9 \\
     & C_141_114_136_8 & 3,350.5 & 19,891.6 & 39.1 & 1,255.8 & 1,366.2 & 2,251.9 & 5,271,698.5 & 19,556.2 & 18.0 & 1,366.7 & 57.9 & 1,380.0 & 2,695.1 & 3,281,568.6 \\
     & C_140_114_132_8 & 3,401.5 & 21,917.6 & 23.8 & 1,254.1 & 680.1 & 3,389.9 & 3,744,172.5 & 22,590.2 & 17.5 & 1,248.5 & 58.7 & 766.3 & 3,267.6 & 3,109,441.2 \\
     & C_143_101_123_8 & 3,437.5 & 23,477.2 & 0.0 & 677.7 & 955.5 & 4,369.4 & 817,244.5 & 23,806.9 & 0.0 & 617.3 & 56.0 & 1,302.2 & 5,147.9 & 783,123.1 \\
     & C_137_112_129_8 & 3,471.0 & 22,089.2 & 0.0 & 546.6 & 544.8 & 4,187.3 & 668,737.0 & 21,195.2 & 0.0 & 456.6 & 55.0 & 883.9 & 3,532.1 & 574,935.0 \\

>>>>

\begin{abstract}
    This paper addresses a novel variant of the Concrete Delivery Problem (CDP), which involves the efficient scheduling of ready-mixed concrete deliveries to construction sites while balancing the conflicting goals of minimizing transportation costs and maximizing customer satisfaction. In this study, we propose an exact formulation and a heuristic approach based on the Greedy Randomized Adaptive Search Procedure (GRASP), to tackle this challenging CDP variant. This variant introduces realistic side constraints, including driver working shifts, a minimum driver working time, and overtime penalties. Additionally, it considers the scenario where customers may request multiple types of concrete delivered within the same time window. We assess the performance of our heuristic using new public instances generated for this problem and provide a comparative analysis with another CDP variant to demonstrate its effectiveness.
\end{abstract}

@@

\section{Introduction}
\label{sec:cdp_intro}
Concrete is a widely used building material in construction projects. Its perishable nature is affected by many factors that impact its quality \citep{sinha_quality_2021}, which is crucial for the durability and strength of the final construction. Concrete comes in two types: ready-mixed concrete (RMC) and site-mixed concrete (SMC). RMC is manufactured in a batch plant and delivered to the construction site, while SMC is produced on-site using raw materials stored on the construction site. Using SMC can avoid delays caused by road traffic, but it has a slower and more difficult production process, requires storage for mixing materials and equipment, and is suitable for low amounts of concrete. On the other hand, RMC has better quality and benefits from lower production costs \citep{muresan_comparing}. However, to take advantage of these benefits, the batch plant manager must ensure efficient and prompt delivery on the construction site, which may require a fleet of high-cost revolving drum trucks (concrete mixers) to dispatch the RMC.

@@

The rest of the paper is organized as follows: Section \ref{sec:cdp_lit_review} provides a literature review of previous work related to the CDP. Section \ref{sec:cdp_desc_form} provides a formal description and mathematical model of the problem. Section \ref{sec:cdp_grasp_method} describes the GRASP algorithm and the constructive heuristics developed to solve this variant of the CDP. Section \ref{sec:cdp_comp_exp} presents computational experiments and sensitivity analyses to evaluate the proposed approach, and finally, section \ref{sec:cdp_concl} presents the conclusions.

\section{Literature review}
\label{sec:cdp_lit_review}

@@

\section{Problem description}
\label{sec:cdp_desc_form}
The focus of this paper is on the distribution of RMC from a Canadian company that operates in the greater Montreal area. When a customer places an order, it is received at a control center and immediately assigned to one of the company's batch plants. These plants produce the concrete and then deliver it to the customer. The problem we are examining involves a set of customer orders, a set of concrete-mixer drivers, and a set of batch plants.

@@

@@

\begin{figure}[htbp]
    \centering
    \vspace*{-0mm}
    \begin{adjustbox}{max width=0.85\textwidth}
        \begin{tikzpicture}[-latex]

            \matrix (chart)
            [
            base/.style = {shape=rectangle, 
                      anchor=center,minimum size=5mm, 
                     align=center,
                     top color=white, ,inner sep=0ex,
                     minimum size=5mm
                     },
    LC11/.style =   {  base,   
                    text width=3em, 
                    bottom color=brown!100,
                    },
    UC11/.style = {     base,    
                    text width=5em, 
                    bottom color=brown!100,
                    align = right,
                },
    LC12/.style =   {  base,   
                    text width=1em, 
                    bottom color=orange!100,
                    },
    UC12/.style = {     base,    
                    text width=2.5em, 
                    bottom color=orange!100,
                },
    LC21/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=brown!100,
                    },
    UC21/.style = {     base,    
                    text width=3.5em, 
                    bottom color=brown!100,
                },
    LC22/.style =   {  base,   
                    text width=4em, 
                    bottom color=blue!100,
                    },
    UC22/.style = {     base,    
                    text width=7em, 
                    bottom color=blue!100,
                    align = left,
                },
    UC221/.style = {     base,    
                    text width=3.5em, 
                    bottom color=blue!100,
                    % color=blue!100,
                    outer xsep=0em,
                    % align = right,
                },
                UC231/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=blue!100,
                    },
    LC23/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=orange!100,
                    },
    UC23/.style = {     base,    
                    text width=2.em, 
                    bottom color=orange!100,
                },
  env/.style      = {base, font=\ttfamily\normalsize},
label/.style   = {base,font=\ttfamily\normalsize, text width = 8em, 
  inner sep=0em, rounded corners=1mm,bottom color=red!80,},
  dummy/.style    = {circle,draw},
            matrix of nodes, nodes in empty cells,
            column sep      = 0em,
            row sep         = 3ex,
            column 1/.style = {nodes={label}},    column 2/.style = {},       column 3/.style = {nodes={env}},      column 4/.style = {nodes={env}},         column 5/.style = {nodes={env}},         column 6/.style = {nodes={env}},           column 7/.style = {nodes={env}},           column 8/.style = {nodes={env}},           column 9/.style = {nodes={env}},           column 10/.style = {nodes={env}},         column 11/.style = {nodes={env}},           column 12/.style = {nodes={env}},    column 13/.style = {nodes={env}}
            ]
            {
            $C_2-D_2$ (1 m$^3$) &
            &   &   &   &   &   &   &   &   &   &   &   &            |[LC23]| L &            &       &     |[UC23]| U \\
            $C_2-D_1$ (3 m$^3$) &           &      &        &        &           &            &            &
            &
            &
            &
            |[LC21]| L &
            &
            &
            &
            |[UC21]| U &
            \\
            $C_2-D_3$ (11 m$^3$) &
            &
            &
            &
            &
            &
            |[LC22]| L &
            &
            &
            |[UC22]| &
            |[UC22]|U  &
            |[UC221]|  &
            &
            &
            &
            &
            \\
            $C_1-D_2$ (4 m$^3$) &
            &
            &
            &
            |[LC12]| L &
            &
            &
            &
            |[UC12]| U &
            &
            &
            &
            &
            &
            &
            &
            \\
            $C_1-D_1$ (8 m$^3$) &
            &
            |[LC11]| L &
            &
            &
            &
            |[UC11]|U &
            |[UC11]| &
            &
            &
            &
            &
            &
            &
            &
            &
            \\
            \vspace*{-10em}
            Start time &&
            06:21 &
            &
            06:40 &
            &
            07:00 &
            &
            07:16 &  07:25 &
            &
            07:43 &
            &
            07:51 &
            &
            08:02 & 08:08 \\
            };
            % \node[fit={(chart-3-10) (chart-3-12)},style=UC22]{U};
            \draw (chart-5-3) edge (chart-5-7);
            % \draw (chart-5-8.3) edge (chart-2-12);
            \draw  (chart-4-5) edge (chart-4-9);
            % \draw  (chart-4-9) edge (chart-1-14);
            \draw  (chart-3-7) edge (chart-3-10);
            \draw  (chart-2-12) edge (chart-2-16);
            \draw  (chart-1-14) edge (chart-1-17);

@@

\section{Constructive heuristics and GRASP}
\label{sec:cdp_grasp_method}

@@

\section{Computational experiments}
\label{sec:cdp_comp_exp}

In this section, we present and discuss the results of computational experiments conducted using the GRASP heuristic described in section~\ref{sec:cdp_grasp_method}. The implementation of the GRASP algorithm is coded in C++. We run our experiments on the benchmark data used in \cite{kinable2014concrete}, and on a new dataset extracted from delivery operations records provided by our industry partner.

\subsection{Generation of instances}
\newcommand{\nbInstance}{36}
The dataset used in this section was obtained from our partner and contains records representing delivery operations from up to 8 production centers for $\nbInstance$ days. From this historical data, we extract information such as daily orders delivered, plant assignments to orders, and the number of available drivers. We created $\nbInstance$ instances from this data, where each instance corresponds to a daily operation. To maintain confidentiality, we have removed the GPS coordinates of customers and plants, but have included two matrices containing the distances and driving times between all plants and customers. An instance contains information such as each driver's capacity, associated batch plant, and shift start time (which we generate). For each customer, we have the due time, the total demand, the number of orders (type of concrete) received, and its index in the time (distance) matrix. For each order, we have its demand and the corresponding production plant. Finally, we have the loading capacity for each plant, and also its index in the time matrix. The name of an instance has the format $C\_k\_n\_o\_z$, where $k$ is the number of available drivers, $n$ is the number of customers, $o$ is the total number of daily orders, and $z$ is the number of plants. The dataset is divided into small, medium, and large sets according to the total number of daily orders. We have summarized the dataset in Table~\ref{tab:cdp_instances}. The dataset is available upon request as a contribution to the CDP literature.

\begin{table}[htpb]
    \centering
    \caption{Instances summary}
    \label{tab:cdp_instances}
    \small
    \resizebox*{0.8\textwidth}{!}{
        \begin{tabular}{lcccccc}
            \toprule
            {}     & \# & Demand            & \#Order   & \#Client & \#Driver & \#Depot \\
                   &    & (m$^3$)           &           &          &          &         \\
            \midrule
            Small  & 8  & 226.5 - 937.5     & 7 - 14    & 4 - 11   & 13-35    & 1-3     \\
            % \cmidrule{3-7}
            Medium & 14 & 1,160.5 - 2,971.0 & 43 - 98   & 40 - 89  & 76-137   & 6-8     \\
            % \cmidrule{3-7}
            Large  & 14 & 3,078. - 3,953.5  & 107 - 136 & 92 - 127 & 129-150  & 8       \\
            \bottomrule
        \end{tabular}
    }
\end{table}

@@

\cite{kinable2014concrete} provided a benchmark dataset for their variant of the $CDP$. Although their primary objective is to maximize the total load delivered each day, without considering loading operations at a plant and ensuring deliveries within specified time windows, we still use this dataset to analyze and compare the performance of our algorithm under different conditions. Table \ref{tab:cdp_lit_comp} shows the performance of the GRASP heuristic along with the other methods (CP, MIP, SD-heuristic, and Hybrid) used in \cite{kinable2014concrete}.  For each method, the table shows the average execution time in milliseconds and the corresponding gap between the obtained solution and the upper bound provided by \cite{kinable2014concrete}.

\begin{table}[htbp]
    \centering
    \caption{Performance of the GRASP heuristic on the CDP benchmark instances}
    \label{tab:cdp_lit_comp}
    \scriptsize
    \resizebox{1\textwidth}{!}{
        \begin{tabular}{@{}cccccccccccc@{}}
            \toprule
                                   &     & \multicolumn{2}{c}{CP}     & \multicolumn{2}{c}{MIP}   & \multicolumn{2}{c}{SD-heuristic} & \multicolumn{2}{c}{Hybrid} & \multicolumn{2}{c}{GRASP}                                                            \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
                                   &     & Gap (\%)                   & Time (ms)                 & Gap (\%)                         & Time (ms)                  & Gap (\%)                   & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
            \multirow{2}{*}{Set A} & Avg & 4.2                        & 197,012                   & 7.3                              & 13,405,798                 & 9.1                        & 23        & 7.0      & 100,765   & 5.7      & 13,186    \\ \cmidrule(l){2-10} \cmidrule(l){11-12}
                                   & Opt & \multicolumn{2}{c}{40/64}  & \multicolumn{2}{c}{37/64} & \multicolumn{2}{c}{30/64}        & \multicolumn{2}{c}{35/64}  & \multicolumn{2}{c}{35/64}                                                            \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
            \multirow{2}{*}{Set B} & Avg & 12.1                       & 357,313                   & -                                & -                          & 16.3                       & 1,331     & -        & -         & 13.8     & 574,983   \\ \cmidrule(l){2-10} \cmidrule(l){11-12}
                                   & Opt & \multicolumn{2}{c}{55/128} & \multicolumn{2}{c}{-}     & \multicolumn{2}{c}{40/128}       & \multicolumn{2}{c}{-}      & \multicolumn{2}{c}{44/128}                                                           \\ \bottomrule
        \end{tabular}
    }
\end{table}

@@

The computational results of our instances solved with the GRASP heuristic are summarized in the tables below. %The stopping criteria are set to 20,000 iterations or 3600 seconds of running time (unless otherwise specified).
The parameters used in our experiments are listed in Table~\ref{tab:cdp_problem_parameters}.

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:cdp_problem_parameters}
    \small
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter}  &
        \multicolumn{1}{c}{Value} \\ \midrule
 Time window ($\tau^w$)  & 60 min    \\
 Unloading duration ($\tau_c^u$)  & 2 min$/m^3$   \\
 Cleaning duration ($\rho$)    & 10 min  \\
        Adjustment duration ($\alpha$)                                                & 10 min                    \\
        Max travel time ($\Delta$)                                                    & 120 min                   \\
        Min working time ($M_T$)                                                      & 180 min                   \\
        Max working time ($N_T$)                                                      & 480 min                   \\
        Max overtime duration ($O_T$)                                                 & 120 min                   \\
        Max delay between two consecutive deliveries of the same order $\gamma^1$)   & 20 min                    \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min                    \\
        Penalty of unfulfilled orders ($\beta_1$)                                     & 10,0000                   \\
        Penalty of first delivery delay ($\beta_2$)                                   & 1,0000                    \\
        Penalty for driver underutilization  ($\beta_3$)                              & 30                        \\
        Driver overtime penalty $ (\beta_4$)                                          & 20                        \\
        \bottomrule
    \end{tabularx}
\end{table}

The table \ref{tab:cdp_all_instances} contains the detailed results for all instances with a stop criterion of 3600 seconds. The table shows the demand of each instance, the average, and the best values of the objective function when solving each instance five times. All daily orders of the small instances are completely served by our algorithm within these five iterations, as shown in column $UQ$, which reports the undelivered quantity. For the medium and large instances, $99.57\%$ and $99.5\%$ of the total demands are delivered. The sum of driver underutilization costs ($DUC$) is high for medium and large instances. This indicates the underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase travel costs ($TC$).

@@

    \multirow[c]{14}{*}{Large} & C\_132\_98\_109\_8 & 3,078.5 & 22,994.6 & 0.0 & 465.5 & 496.5 & 3,804.8 & 579,471.0 & 22,712.7 & 0.0 & 351.5 & 56.2 & 803.2 & 4,011.3 & 478,549.4 \\
     & C\_129\_101\_119\_8 & 3,229.0 & 17,323.1 & 11.0 & 657.8 & 1,577.6 & 2,375.9 & 1,869,937.5 & 17,311.8 & 11.0 & 598.8 & 58.4 & 1,507.7 & 1,948.1 & 1,800,315.9 \\
     & C\_141\_114\_136\_8 & 3,350.5 & 19,891.6 & 39.1 & 1,255.8 & 1,366.2 & 2,251.9 & 5,271,698.5 & 19,556.2 & 18.0 & 1,366.7 & 57.9 & 1,380.0 & 2,695.1 & 3,281,568.6 \\
     & C\_140\_114\_132\_8 & 3,401.5 & 21,917.6 & 23.8 & 1,254.1 & 680.1 & 3,389.9 & 3,744,172.5 & 22,590.2 & 17.5 & 1,248.5 & 58.7 & 766.3 & 3,267.6 & 3,109,441.2 \\
     & C\_143\_101\_123\_8 & 3,437.5 & 23,477.2 & 0.0 & 677.7 & 955.5 & 4,369.4 & 817,244.5 & 23,806.9 & 0.0 & 617.3 & 56.0 & 1,302.2 & 5,147.9 & 783,123.1 \\
     & C\_137\_112\_129\_8 & 3,471.0 & 22,089.2 & 0.0 & 546.6 & 544.8 & 4,187.3 & 668,737.0 & 21,195.2 & 0.0 & 456.6 & 55.0 & 883.9 & 3,532.1 & 574,935.0 \\
